---
title: "Final Project: Masculinity Survey"
format: 
  html:
    theme: solar
execute:
  echo: false
---
Class: EPI 590R: R Bootcamp

Student: Anna Tramposch

``` {r}
#| message: FALSE

library(tidyverse)
library(here)
library(gtsummary)
library(readr)
library(dplyr)
library(broom.helpers)
library(ggplot2)
```

``` {r}
#| message: FALSE
# Read in the raw data

masculinity_rawdata <- read_csv(here("data", "raw", "raw-responses.csv"))
```

```{r}
# Create a subset from the raw data

masculinity_subset <- masculinity_rawdata %>%
		rename(StudyID = ...1,
					 FeelingMasculine = q0001,
					 PerceiveMasculine = q0002,
					 FatherModel = q0004_0001,
					 MotherModel = q0004_0002,
					 OtherFamily = q0004_0003,
					 PopCulture = q0004_0004,
					 Friends = q0004_0005,
					 SocietyPressure = q0005,
					 Employment = q0009,
					 MaritalStatus = q0024,
					 KidUnder18 = q0025_0001,
					 KidOver18 = q0025_0002,
					 NoKids = q0025_0003,
					 KidsGeneral = kids,
					 SexualOrient= q0026,
					 Age = age3,
					 Race = q0028,
					 School = q0029,
					 Income = q0034) %>%
	mutate(MaritalStatus_cat = factor(MaritalStatus, labels = c("Divorced", "Married", "Never married", "No answer", "Separated", "Widowed")),
        	KidsGeneral_cat = factor(KidsGeneral, labels = c("Has Children", "No Children")),
        	SexualOrient_cat = factor(SexualOrient, labels = c("Bisexual", "Gay", "No answer","Other", "Straight")),
        	Age_cat = factor(Age, labels = c("18 - 34", "35 - 64", "64 and up")),
        	Race_cat = factor(Race, labels = c("Asian", "Black", "Hispanic", "Other", "White")),
        	School_cat = factor(School, labels = c("Associate's degree", "College graudate", "Did not complete high school", "High school or G.E.D", "Post graduate degree", "Some college")),
					Income_cat = factor(Income, labels = c("$0-$9.9k", "$10k - $24.9k", "$100k - 124.9k", "$125k - $149.9k", "$150k - $174.9k", "$175k - $199.9k", "$200k plus", "$25k - $49.9k", "$50k - $74.9k", "$75k - $99.9k", "No answer"))
					) %>%
	select("StudyID", "FeelingMasculine", "PerceiveMasculine",
								"FatherModel", "MotherModel", "OtherFamily", "PopCulture",
								"Friends", "SocietyPressure", "Employment", "MaritalStatus", 
								"KidUnder18", "KidOver18", "NoKids", "KidsGeneral",
								"SexualOrient", "Age", "Race", "School", "Income", 
								"MaritalStatus_cat", "KidsGeneral_cat", "SexualOrient_cat", "Age_cat", "Race_cat", "School_cat", "Income_cat")

str(masculinity_subset)

```


``` {r}
#| results: 'hide'

# Check that the Factor labels applied correctly
table(masculinity_subset$MaritalStatus)
table(masculinity_subset$MaritalStatus_cat)
table(masculinity_subset$KidsGeneral)
table(masculinity_subset$KidsGeneral_cat)
table(masculinity_subset$SexualOrient)
table(masculinity_subset$SexualOrient_cat)
table(masculinity_subset$Age)
table(masculinity_subset$Age_cat)
table(masculinity_subset$Race)
table(masculinity_subset$Race_cat)
table(masculinity_subset$School)
table(masculinity_subset$School_cat)
table(masculinity_subset$Income)
table(masculinity_subset$Income_cat)
```

This data set contains the results of a survey of 1,615 adult men conducted by SurveyMonkey in partnership with FiveThirtyEight and WNYC Studios from May 10-22, 2018. The modeled error estimate for this survey is plus or minus 2.5 percentage points. The percentages have been weighted for age, race, education, and geography using the Census Bureau’s American Community Survey to reflect the demographic composition of the United States age 18 and over. Crosstabs with less than 100 respondents have been left blank because responses would not be statistically significant.

# Table One
``` {r}
#| label: tbl-one
#| tbl-cap: "Study Population Characteristics"

# Create a gtsummary

table1 <- tbl_summary(
		masculinity_subset,
		by = NULL,
		include = c("FeelingMasculine", "PerceiveMasculine", "SocietyPressure", "MaritalStatus_cat", "KidsGeneral_cat", "SexualOrient_cat", "Age_cat", "Race_cat", "School_cat", "Income_cat"),
		label = list(
			FeelingMasculine ~ "How Masculine I Feel",
			PerceiveMasculine ~ "How Important Others See Me as Masculine",
			SocietyPressure ~ "Does Society Put Unhealthy Pressure On Men",
			MaritalStatus_cat ~ "Marital Status",
			KidsGeneral_cat ~ "Kids Status",
			SexualOrient_cat ~ "Sexual Orientation",
			Age_cat ~ "Age",
			Race_cat ~ "Race",
			School_cat ~ "Education",
			Income_cat ~ "Income")
)

table1
```
@tbl-one shows there were `r inline_text(table1, variable = "FeelingMasculine", level="Very masculine")` of `r nrow(masculinity_subset)` study respondents who reported feeling "Very Masculine"


# Regression Table
``` {r}
#| message: FALSE
#| label: tbl-two
#| tbl-cap: "Assocation between Feelings of Masculinity and Various Study Characteristics"

tbl_uvregression(
	masculinity_subset,
	x = FeelingMasculine,
	include = c(MaritalStatus_cat, KidsGeneral_cat, SexualOrient_cat, Age_cat,
							Race_cat, School_cat, Income_cat),
	method = lm)

```


# Figure 1
``` {r}
#| label: fig-plot
#| fig-cap: "This is a bar plot of the age among study particpants"

Age_barplot <- ggplot(masculinity_subset, aes(x = Age_cat)) +
  geom_bar() +
  ggtitle("Age Among Masculinity Survey Respondents") +
  xlab("Age Bracket") +
  ylab("Numbner of Respondents")

print(Age_barplot)

totalstudy <- nrow(masculinity_subset)
```

``` {r}
#| message: FALSE

ggsave(Age_barplot, file = here("results", "Age_barplot.png"))

```

@fig-plot shows that of `r totalstudy` participants in the study, `r sum(masculinity_subset$Age_cat=='18 - 34')` reported they were between 18 and 34 years of age.
 

# Create a Function
``` {r}
count_factor <- function(factor_var) {
  freq_table <- table(factor_var)
  freq_df <- as.data.frame(freq_table)
  colnames(freq_df) <- c("Level", "Frequency")
  return(freq_df)
}

count_factor(masculinity_subset$Income_cat)
```
